---
title: "Classify Data Using Logistic Regression"
author: "Laura Cline"
date: "13/03/2021"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Install and load libraries
library(Rserve)
# Rserve()
```

# Create a Logistic Regression Model in R 

```{r}
# Load Data
train_data <- read.csv("data/TrainingData.csv")
test_data <- read.csv("data/TestData.csv")
```

```{r}
# Create the logistic regression model 
model3 <- glm(LastYear ~ Year1 + Year2 + Year3 + Year4 + Year5, data = train_data, family = binomial)

model3
```

```{r}
# Test our logistic regression model
test_data$pred <- predict(model3, newdata = test_data, type = "response")

summary(model3)
```

# Add an R Logistic Regression to a Tableau Viz 

1. Create a table in Tableau. Drag the Patron ID to the Rows shelf and Drag Years 1 through 5 to the data area.

2. Create a calculated field: 

SCRIPT_REAL(
'train_data <- read.csv("data/TrainData.csv")
model3 <- glm(.arg1 ~ .arg2 + .arg3 + .arg4 + .arg5 + .arg6, data = train_data, family = binomial)
test_data <- read.csv("data/TestData.csv")

result <- predict(model3, newdata = test_data, type = "response")',

SUM([Last Year]), SUM([Year1]), SUM([Year2]), SUM([Year3]), SUM([Year4]), SUM([Year5])
)

3. Drag the new calculated field to the Measure Values card below Year 5. 