---
title: "Create and Visualize Linear Regression Models"
author: "Laura Cline"
date: "13/03/2021"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# install.packages("Rserve")
library(Rserve)
```

```{r}
# Rserve()
```

# Create a Single and Multiple-Variable Linear Regression Model in R 

```{r}
# Load data 
sales_data <- read.csv("data/SalesData.csv")
```

```{r}
# Create single variable linear regression model 
model1 <- lm(sales_data$Sales ~ sales_data$Distance, data = sales_data)

model1
```
```{r}
summary(model1)
```

```{r}
# Create a multiple variable linear regression 

model2 <- lm(sales_data$Sales ~ sales_data$Distance + sales_data$OrderCount, data = sales_data)

model2
```

```{r}
summary(model2)
```

# Add an R Regression Model to Tableau Viz 

1. Create a scatterplot with Order Count in columns and Sales in rows. Go to the Analysis tab and turn off aggregate measures. 

2. Create a calculated field in Tableau. In the calculated field write: 

SCRIPT_REAL(
"model <- lm(.arg1 ~ .arg2 + .arg3)
model$fitted",

SUM([Sales]), SUM([Distance]), SUM([Order Count])
)

3. Drag the calculated field to the y-axis. 